
\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\ci#1{\textcircled{\resizebox{.5em}{!}{#1}}}

\namesection{Leon}{Adato}{% 
\Large{Developer Relations Advocate} \linebreak
\large \vspace{\topsep}
\faGithub \ \href{https://github.com/adatole}{LeonAdato} | \faLinkedin \ \href{https://www.linkedin.com/in/adatole/}{LeonAdato} | \faTwitter \ \href{https://twitter.com/LeonAdato}{LeonAdato} | \faMastodon \ \href{https://infosec.exchange/@leonadato}{@leonadato@infosec.exchange}
\linebreak
\faEnvelope \ \href{mailto:leon@adatosystems.com}{leon@adatosystems.com} | 
\faPhone \ 216-202-LEON | 
\faBlog \ \href{https://adatosystems.com}{AdatySystems.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE (was column two)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.64\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Personal Projects \& Content}
\descript{ }
\begin{tightemize}
	\vspace{\topsep}
	\item Author: "The Four Questions Every Monitoring Engineer is Asked"
	\item Host: "Technically Religious" podcast
	\item Guest: on multiple series (Cloudbytes, Gestalt IT, IT Reality, \linebreak The Watercooler)
	\item Speaker: DevOpsDays, Monitorama, CloudNative, \& more
	\item Speaker info: \href{http://www.adatosystems.com/speaking/}{\location{http://www.adatosystems.com/speaking/}}
	\item Full list of work: \linebreak \href{http://www.adatosystems.com/articles-and-appearances/}{\location{http://www.adatosystems.com/articles-and-appearances/}}
\end{tightemize}
\sectionsep

\runsubsection{Principal Developer Relations Advocate}
\descript{}
\location{11/2021 - Present | New Relic | San Francisco, CA}
\begin{tightemize}
	\item Promoted, contextualized, and amplified brand and technical position, use cases, and key concepts; Internal advocate for customer needs and feature requests.
	\item Created in-depth technical content for brand-hosted and external online publications; produced deep-dive technical videos.
	\item Wrote, organized, hosted, and provide post-production for video series.
	\item Participated at conferences as an invited speaker; as part of boothstaff; and as a workshop instructor.
	\item Per year: 25-40 essays, 1-2 ebooks, 10-20 video assets, and 5-10 conventions/user groups.
\end{tightemize}
\sectionsep

\runsubsection{"Head Geek"/Principal Technical Marketing Mgr}
\descript{}
\location{08/2014 - 11/2021 | SolarWinds | Austin, TX}
\begin{tightemize}
	\item External promotion, contextualizing, and amplification of monitoring concepts and use cases; Internal advocate for customer needs, with contributions generating \$2m per year in measurable revenue.
	\item Created in-depth technical content for external online and print \linebreak publications; and internal training, knowledge sharing, and follow-on assets during the sales motion.
	\item Per year: 50-80 essays, 2-4 ebooks, 20-40 video assets, and 5-10 conventions/user groups.
\end{tightemize}
\sectionsep

\runsubsection{Sr. Consultant - Monitoring}
\descript{}
\location{11/2011 - 08/2014 | Cardinal Health | Columbus, OH}
\begin{tightemize}
	\item Responsible for architectural vision and execution of monitoring solution across ~10k devices. Reduced monitoring spend by \$700k per yr while doubling capability.
\end{tightemize}
\sectionsep

\runsubsection{Systems Monitoring Engineer}
\descript{}
\location{05/2010 - 11/2011 | Sentinel Technologies | Chicago, IL}
\begin{tightemize}
	\item Designed and implemented a monitoring-as-a-service solution. Implemented design in 90 days.
\end{tightemize}

\end{minipage}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO (was column one)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{OS and Std. Applications}
\textbullet{}DOS (yes, it's called DOS)
\textbullet{}Unix (HP-UX, AIX, Solaris)
\textbullet{}Linux (various distros)\linebreak
\textbullet{}Windows server (NT through 2019)
\textbullet{}Windows desktop (286 through 11)
\textbullet{}MS-SQL Server
\textbullet{}MySQL\linebreak
\textbullet{}VirtualBox, VMWare, MS Hyper-V
\textbullet{}Video editing (KDenLive)
\textbullet{}Audio editing (Audacity)
\textbullet{}Content editing
\vspace{\topsep}

\subsection{Programming}
\textbullet{}Python
\textbullet{}PHP
\textbullet{}Javascript
\textbullet{}Perl
\textbullet{}SQL
\textbullet{}CSS/HTML/Markdown
\textbullet{}Shell, DOS batch, cmdline, Office macros
\textbullet{}\LaTeX 
\vspace{\topsep}

\subsection{Monitoring \& O11y}
\textbullet{}New Relic
\textbullet{}SolarWinds
\textbullet{}BMC Patrol
\textbullet{}HP OpenView
\textbullet{}Nagios
\textbullet{}net-SNMP
\textbullet{}Syslog-ng
\vspace{\topsep}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Certifications}
\textbullet{}SolarWinds Certified Professional
\textbullet{}CompTia A+: 2017
\textbullet{}MCSE: Win2003+Messaging, 2005
\textbullet{}Cisco CCNA: 2004
\textbullet{}MCSE: NT4, 1999
\textbullet{}WordPerfect: 1989
\textbullet{}SAFD: 1988
\sectionsep
\subsection{New York University}
\descript{Bachelors of Fine Arts (w/Honors): 1989}
\vspace{\topsep}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Languages}
\textbullet{}English
\textbullet{}ASL
\textbullet{}Spanish
\textbullet{}French
\textbullet{}Hebrew
\textbullet{}Geek/Nerd

\end{minipage} 

\end{document}